---
author:"UMER TAHIR"
title: "coursera_data"
---

## COURSERA RECORD

This dataset is about the record of Coursera which is global online platform that offers anyone, anywhere access to online courses provided by different organization. It contains mainly 6 columns and 891 observations.

1.  **Course_title :** Contains the course title.

2.  **Course_organization** : It tells which organization is conducting the courses.

3.  **Course_Certificate_type :** It has details about what are the different certifications available in courses.

4.  **Course_rating :** It has the ratings associated with each course.

5.  **Course_difficulty :** It tells about how difficult or what is the level of the course.

6.  **Course_students_enrolled :** It has the number of students that are enrolled in the course.

    ```{r}
    install.packages("readr")
    ```

```{r}
library(readr)
Coursera_data<- read_csv("data/Coursera.csv")
colnames(Coursera_data)


```

```{r}
install.packages("tibble")
```

```{r}
library(tibble)
data<-as_tibble(Coursera_data)
data
```

```{r}
data<-data[-1]
```

```{r}
library(tibble)
glimpse(data)


```
```{r}
library(ggplot2)
#data$course_difficulty <- factor(data$course_difficulty, levels = c("Beginner", "Intermediate", "Advanced", "Mixed"))
ggplot(data,aes(x=factor(course_difficulty,levels = unique(course_difficulty))))+
  geom_bar(position="dodge",width=0.5,fill=c("lightblue", "yellow","pink","violet"))+
  #scale_colour_manual(values = c("lightblue", "yellow","pink","violet"))+
  
  theme_minimal()
  


```

**PLOT 1:**

My first plot is about the course difficulty level in different type of certificates. We have three certificate type and four difficulty level of these certificates.

```{r}
library(ggplot2)
data$course_difficulty <- factor(data$course_difficulty, levels = c("Beginner", "Intermediate", "Advanced", "Mixed"))
ggplot(data, aes(x = course_difficulty, fill = course_Certificate_type)) +
  geom_bar(position = "dodge") +
  #geom_bar(aes(x = course_difficulty, fill = course_Certificate_type,position="dodge"))+
  scale_fill_manual() +
  labs(title = "Course Difficulty level by Certificate Type",
       x="COURSE DIFFICULTY",
       y="Total Number")+
  scale_y_continuous(breaks = seq(0, 300, by = 30), limits = c(0, 300))



```

```         
```
```{r}
library(ggplot2)

# Get the top 10 course organizations
top_10_organizations <- names(sort(table(data$course_organization), decreasing = TRUE))[10:1]

# Reorder the levels of course_organization based on count
data$course_organization <- factor(data$course_organization, levels = top_10_organizations)

# Filter the data for the top 10 organizations
data_top_10 <- data[data$course_organization %in% top_10_organizations, ]

# Plotting
ggplot(data_top_10, aes(y = course_organization)) +
  geom_bar(fill="pink", width = 0.5) +
  scale_fill_brewer(palette = "Set3") +
  geom_text(stat = 'count', aes(label = ..count..), vjust = 0.1) +
  theme_minimal() +
  labs(title = 'Top 10 Course Organizations', x = 'Number Of courses', y = 'Top Organizations') +
  theme(axis.text.y = element_text(angle = 0, hjust = 1)) +
  scale_x_continuous(limits = c(0, 70), breaks = seq(0, 70, by = 10))

```
```{r}
# Install and load the necessary library
#install.packages("ggplot2")
library(ggplot2)

# Get the top 10 course organizations
top_10_organizations <- head(names(sort(table(data$course_organization), decreasing = TRUE)), 10)

# Filter the data for the top 10 organizations
data_top_10 <- data[data$course_organization %in% top_10_organizations, ]

# Plotting
ggplot(data_top_10, aes(y = course_organization)) +
  geom_bar(fill="pink",width=0.5) +
  scale_fill_brewer(palette = "set3")+
  geom_text(stat = 'count', aes(label = ..count..), vjust = 0.1
            
            
            ) +
  theme_minimal() +
  labs(title = 'Top 10 Course Organizations', x = 'NUmber Of courses', y = 'Top Organizations') +
  theme(axis.text.y = element_text(angle =360, hjust = 1))+
  scale_x_continuous(limits = c(0, 70), breaks = seq(0, 70, by = 10))
  
  #scale_y_continuous(breaks = seq(0, 300, by = 50), limits = c(0, 300)))


```

```{r}
library(ggplot2)

# Plotting a histogram using ggplot2
ggplot(data, aes(x = course_rating))+
  geom_bar(fill="blue")+
  theme_minimal() 
  #theme(legend.position = "top") +
  #scale_x_discrete(limits = as.character(seq(4, 5, by = 0.2)))


              

```

PLOT 2:

This plot shows the number of difficulty level corresponding to each Course ratting.

```{r}
ggplot(data, aes(x = as.factor(course_rating), fill = course_difficulty)) +
  geom_bar(position = position_dodge2(preserve = "single")) +
  labs(title = "Count Plot of Course Ratings by Difficulty Level",
       x = "Course Rating",
       y = "Count") +
  theme_minimal() +
  #theme(legend.position = "top") +
  scale_x_discrete(limits = as.character(seq(4, 5, by = 0.1)))+
  scale_y_continuous(breaks = seq(0, 45, by = 5), limits = c(0, 45))

```
```{r}
max_students_index <- which.max(data$students_enrolled)

# Get the record with the highest number of students enrolled
record_highest_enrollment <- data[max_students_index, ]

# Print the record
print(record_highest_enrollment)
library(ggplot2)

# Sort the data by the number of students enrolled in descending order
data_sorted <- data[order(-data$students_enrolled), ]

# Select the top 10 courses
top_10_courses <- head(data_sorted, 10)

# Plotting
ggplot(top_10_courses, aes(x = reorder(course_title, -students_enrolled), y = students_enrolled)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  labs(title = 'Top 10 Courses with Highest Enrollments', x = 'Course Title', y = 'Number of Students Enrolled') +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

```{r}
# Sort the data by course rating in descending order
data_sorted_by_rating <- data[order(-data$course_rating), ]

# Select the top 10 courses
top_10_courses_by_rating <- head(data_sorted_by_rating, 10)

# Plotting
ggplot(top_10_courses_by_rating, aes(x = reorder(course_title, -course_rating), y = course_rating)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  labs(title = 'Top 10 Courses with Highest Ratings', x = 'Course Title', y = 'Course Rating') +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


```

```{r}
# Assuming df is your data frame

# Install and load the necessary library

library(ggplot2)

# Plotting
ggplot(data, aes(x = course_rating)) +
  geom_point(stat = "count", aes(y = ..count..), position = position_jitter(width = 0.1)) +
  labs(title = 'Number of Courses for Each Rating', x = 'Course Rating', y = 'Number of Courses') +
  theme_minimal()


```
```{r}
colnames(data)
```

