---
title: "coursera_data"
Author: "UMER TAHIR"
---

## COURSERA RECORD

This dataset is about the record of Coursera which is global online platform that offers anyone, anywhere access to online courses provided by different organization. It contains mainly 6 columns and 891 observations.

1.  **Course_title :** Contains the course title.

2.  **Course_organization** : It tells which organization is conducting the courses.

3.  **Course_Certificate_type :** It has details about what are the different certifications available in courses.

4.  **Course_rating :** It has the ratings associated with each course.

5.  **Course_difficulty :** It tells about how difficult or what is the level of the course.

6.  **Course_students_enrolled :** It has the number of students that are enrolled in the course.

    ```{r}
    install.packages("readr")
    ```

```{r}
library(readr)
Coursera_data<- read_csv("data/Coursera.csv")
colnames(Coursera_data)


```

```{r}
install.packages("tibble")
```

```{r}
library(tibble)
data<-as_tibble(Coursera_data)
data
```

```{r}
data<-data[-1]
```

```{r}
library(tibble)
glimpse(data)


```
**PLot1**
The analysis start with a plot of showing the number of courses in different course difficulty level.
```{r}
library(ggplot2)
ggplot(data,aes(x=factor(course_difficulty,levels = unique(course_difficulty))))+
  geom_bar(position="dodge",width=0.3,fill=c("yellow", "lightblue","pink","violet"))+
  geom_text(
    stat = "count", 
    aes(label = ..count..), 
    position = position_dodge(width = 0.3), 
    vjust = 0
  ) +
  theme_minimal()+
  labs(title = "Course Distribution Across Difficulty Levels",
       x="COURSE DIFFICULTY",
       y="Total Number")+
  theme(
    plot.title = element_text(hjust = 0.5)
  )
  
  


```

**PLOT **

This plot is about the course difficulty level in different type of certificates. We have three certificate type and four difficulty level of these certificates.

```{r}
library(ggplot2)
ggplot(data, aes(x = course_difficulty, fill = course_Certificate_type)) +
  geom_bar(position = "position_dodge2"(preserve = "single"))+
  theme_minimal()+
  labs(
    title = "Distribution of Courses by Difficulty Level and Certificate Type",
    x = "COURSE DIFFICULTY",
    y = "Total Number"
  ) 
  



```

         
**Plot**
This plot is showing the top ten organizations which offered more courses on coursera.
```{r}
library(ggplot2)

# Get the top 10 course organizations
top_10_organizations <- names(sort(table(data$course_organization), decreasing = TRUE))[10:1]

# Reorder the levels of course_organization based on count
data$course_organization <- factor(data$course_organization, levels = top_10_organizations)

# Filter the data for the top 10 organizations
data_top_10 <- data[data$course_organization %in% top_10_organizations, ]

# Plotting
ggplot(data_top_10, aes(y = course_organization)) +
  geom_bar(fill="skyblue", width = 0.5) +
  geom_text(stat = 'count', aes(label = ..count..), vjust = 0.1) +
  theme_minimal() +
  labs(title = 'Top 10 Course Organizations', x = 'Number Of courses', y = 'Top Organizations') +
  theme(axis.text.y = element_text(angle = 0, hjust = 1)) +
  scale_x_continuous(limits = c(0, 70), breaks = seq(0, 70, by = 10))

```

**Plot**
This plot shows the overall course rating of different courses offered by the coursera.

```{r}
library(ggplot2)

ggplot(data, aes(x = "", y = course_rating)) +
  geom_violin(fill = "lightblue", color = "blue") +
  theme_minimal() +
  labs(
    title = "Distribution of Course Ratings",
    x = NULL,  # Removing x-axis label for better presentation
    y = "Course Rating"
  )

              

```

**PLOT**

This plot Top ten organization with most number of students enrolled.


```{r}
max_students_index <- which.max(data$students_enrolled)

record_highest_enrollment <- data[max_students_index, ]

print(record_highest_enrollment)
library(ggplot2)

# Sort the data by the number of students enrolled in descending order
data_sorted <- data[order(-data$students_enrolled), ]

# Select the top 10 courses
top_10_courses <- head(data_sorted, 10)
ggplot(top_10_courses, aes(x = reorder(course_title, -students_enrolled), y = students_enrolled)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black",width=0.5) +
  labs(title = 'Top 10 Courses with Highest Enrollments', x = 'Course Title', y = 'Number of Students Enrolled') +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```





